An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-23 paper.tex
Simplify complexity analysis
Given all the trouble we went through to prove Theorem 1, the same
machinery now gives us the complexity essentially for free.

\begin{thm}[Correctness of the evolving graph BFS]
Let $G_n$ be an evolving graph and $(v_1, t_1)$ be an active node of $G_n$.
Then Algorithm~\ref{alg:bfs} discovers every active node that is reachable from
the root $(v_1, t_1)$, and $reached[(v, t)]$ is the distance from $(v_1, t_1)$
to $(v, t)$.
\end{thm}

@@

\subsection{Analysis}
\label{sec:analysis}

As presented, the BFS over evolving graphs makes no assumptions about how the% adjacency matrices
Suppose $G_n$ is represented by adjacency lists.
Then the number of adjacency lists is the same as the number
of active nodes in $G_n$. So for large $n$, this representation
can use a large amount of memory.
For the graph $G^{[i]} = (V^{[i]}, E^{[i]})$ at time stamp $i$,
we denote the active node set of $V^{[i]}$ as $\tilde V^{[i]}$,
where we have $\tilde V^{[i]} \subseteq V^{[i]}$.
Step $10$ of  Algorithm \ref{alg:bfs} ensures each active node-time stamp pair in $G_n$ is enqueued in $next$ (and then $frontier$) at most once.
And so \texttt{forward-neighbors} loops through each
active node-time stamp pair at most once.
The operations of enqueuing take $O(1)$ time.
Thus the total operations of enqueuing are
$O(\sum_{i=1}^n|\tilde V^{[i]}|)$, where $|\cdot|$ represents the number of elements of a set.  Let $\sum_i |\tilde V^{[i]}| = |\tilde V|$ and $\sum_i |E^{[i]}| = |\hat E|$.
Then the time of scanning
\texttt{forward-neighbors} is
\[
\sum_{i=1}^n\sum_{v \in \tilde V^{[i]}} \texttt{forward-neighbors}(v) =
O(|\hat E|),
\]
by the definition of forward-neighbors.
Hence the total running time is $O(|\hat E|+ |\tilde V|)$.

>>>>

\begin{thm}[Correctness of the evolving graph BFS]
Let $G_n$ be an evolving graph and $(v_1, t_1)$ be an active node of $G_n$.
Then Algorithm~\ref{alg:bfs} discovers every active node that is reachable from
the root $(v_1, t_1)$, and $reached[(v, t)]$ is the distance from $(v_1, t_1)$
to $(v, t)$.
\label{thm:correct}
\end{thm}

@@

As presented, the BFS over evolving graphs makes no assumptions about how the
evolving graph $G_n$ is represented. Suppose it is represented by a collection of
adjacency lists, one for each active node in $G_n$. Then we have that the
asympotic complexity of BFS on $G_n$ is the same as that for BFS on $G$, using
the 1-1 construction of $G$ from $G_n$.

\begin{thm}[Complexity of the evolving graph BFS]
Let $G_n$ be an evolving graph represented using adjacency lists,
$(v_1, t_1)$ be an active node of $G_n$, and $G=(V,E)$ be the static graph
constructed from $G_n$ using the 1-1 correspondences defined in the proof of
Theorem~\ref{thm:correct}. Then the asymptotic complexity of
Algorithm~\ref{alg:bfs} is $O(|E| + |V|)$.
\end{thm}

\IEEEproof
Any edge in any edge set of $G_n$ can be accessed in constant time in random
access memory. By construction, BFS on $G_n$ is in 1-1 correspondence with BFS
on the static graph $G$. The number of operations of BFS on $G$ is $O(|E| + |V|)$,
and so the result follows.
\endproof
